\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}

\definecolor{lithosblue}{RGB}{59,130,246}
\definecolor{darkgray}{RGB}{55,65,81}

\begin{document}

\thispagestyle{empty}
\begin{center}
    \vspace*{1.5cm}
    {\Huge \textbf{Lithos AI}}\\[0.35cm]
    {\Large Feature-Only Product Snapshot}\\[0.35cm]
    {\large November 2025}\\[2cm]
    {\small ``Two pages of exactly what users get.''}
\end{center}

\newpage
\setcounter{page}{1}

\section*{Platform Pillars}

\begin{itemize}
    \item \textbf{Global Mining Intelligence Index:} Ingests filings from ASX, SEDAR, EDGAR, LSE, plus NI 43-101/JORC/SAMREC reports, ESG disclosures, drill logs, and offtake contracts within 15 minutes of publication.
    \item \textbf{Domain-Tuned LLM Fabric:} 1M+ document corpus powering retrieval-augmented copilots for resource extraction, red-flag monitoring, and memo drafting with cited references.
    \item \textbf{Workflow Automation Mesh:} Event bus that pushes structured outputs into Excel, Snowflake, Slack, DealCloud, and custom APIs with approval controls and audit logging.
\end{itemize}

\section*{Tier Highlights}

\begin{center}
\begin{tabular}{|p{0.18\linewidth}|p{0.26\linewidth}|p{0.26\linewidth}|p{0.26\linewidth}|}
\hline
\textbf{Sphere} & \textbf{Basic} & \textbf{Pro} & \textbf{Enterprise} \\
\hline
Data Access & Watchlists, 15+ filters, inline filing viewer & AI-extracted metrics, historical deltas, bulk downloads & Firm-wide data warehouse sync, streaming updates \\
\hline
AI Features & Smart search, instant highlight reels & Diligence memos, anomaly detection, scenario packs & Custom copilots tied to internal knowledge bases \\
\hline
Automation & Manual exports (CSV, PDF) & One-click memo + model builders & Event-driven workflows into CRM/BI, role-based approvals \\
\hline
Governance & Single-user auth, email alerts & Shared workspaces, SSO, staging API keys & Full IAM, field-level permissions, audit trails, DLP hooks \\
\hline
\end{tabular}
\end{center}

\section*{Feature Inventory}

\subsection*{A. Screening \& Discovery}
\begin{itemize}
    \item Multi-factor screener with 100+ filters (jurisdiction, stage, grades, ESG flags, permitting status).
    \item Infinite-scroll grids with pinned columns, conditional formatting, and saved views per analyst.
    \item Global activity map with satellite overlays for infrastructure, port proximity, and jurisdiction risk.
    \item Real-time alerting (email, Slack) for filings, drill results, management changes, and price-sensitive news.
\end{itemize}

\subsection*{B. Project Deep Dives}
\begin{itemize}
    \item Auto-generated executive summary cards (NPV, IRR, payback, throughput) with provenance links.
    \item Tabbed view: Overview, Technical, Financial, Documents, ESG, AI Insights, Experts.
    \item Side-by-side comparison up to five projects with delta indicators, waterfall charts, and spider plots.
    \item Drill log viewer with structured intercepts, grade-thickness calculators, and lithology tagging.
\end{itemize}

\subsection*{C. AI Copilots}
\begin{itemize}
    \item Natural-language queries returning cited passages and structured tables.
    \item Multi-document synthesis for NI 43-101 bundles, ESG filings, and offtake contracts.
    \item Auto red-flag generator covering permitting risk, metallurgical concerns, capex overruns, and ESG controversies.
    \item Memo studio templates (investment briefs, board updates, lender memos) with firm branding.
\end{itemize}

\subsection*{D. Financial Modeling}
\begin{itemize}
    \item Mining-specific DCF blocks with commodity curves, recovery sliders, and Monte Carlo runs.
    \item Cost curve visualizations and benchmarking across regions, projects, or operators.
    \item Sensitivity lab enabling batch runs across grade, recovery, capex, FX, and discount rate assumptions.
    \item Excel/Sheets add-ins that refresh Lithos data with traceable formulas.
\end{itemize}

\newpage

\subsection*{E. Collaboration \& Governance}
\begin{itemize}
    \item Multi-user workspaces with assignments, comment threads, and @mentions.
    \item Version-controlled scenarios; ability to fork AI outputs for human edits with compare mode.
    \item Knowledge graph linking teams, experts, documents, and deal notes per project.
    \item Audit-ready logging (who read/exported what, AI prompts/responses, data lineage).
\end{itemize}

\subsection*{F. Automations \& Integrations}
\begin{itemize}
    \item Out-of-the-box connectors for Slack, Teams, DealCloud, Salesforce, HubSpot, Snowflake, and REST APIs.
    \item Trigger builder: "If filing drops $\rightarrow$ run AI extraction $\rightarrow$ push memo to CRM $\rightarrow$ notify channel."
    \item Webhook subscriptions with retry logic, dead-letter queues, and schema versioning.
    \item Marketplace for logistics partners, consultants, and labs to plug structured updates back into Lithos.
\end{itemize}

\subsection*{G. Marketplace Extensions}
\begin{itemize}
    \item Geological Analysis Module with cross-sections, assay harmonization, and Competent Person-ready exports.
    \item Referral network for shipping, customs, and warehousing providers, including status tracking inside project timelines.
    \item Deal introduction workflows for explorers, mid-tier miners, and offtakers with configurable success fees.
\end{itemize}

\section*{Monitoring \& Reliability}
\begin{itemize}
    \item 24/7 API monitoring, latency dashboards, and SLA alerts visible to customers.
    \item Data freshness badges denoting ingest timestamps and AI confidence intervals.
    \item Quality review queue with human override for critical metrics; customers can submit inline corrections.
\end{itemize}

\section*{Feature Delivery Roadmap (Snapshot)}
\begin{itemize}
    \item \textbf{Live:} Screener 2.0, AI memo studio, Monte Carlo engine, Slack/DealCloud pushes.
    \item \textbf{Coming in Q1 2026:} In-app geospatial change detection, Snowflake secure data share, automated ESG scoring.
    \item \textbf{Coming in Q2 2026:} Logistics marketplace SLA tracking, on-platform deal rooms, multilingual copilots (ES/FR/PT).
\end{itemize}

\vspace{2cm}

\begin{center}
    \textit{Lithos AI --- Feature depth to collapse diligence, end-to-end.}\\[0.5cm]
    \textbf{Demo:} \href{https://lithosmain-git-main-anishkganeshs-projects.vercel.app/login}{lithosmain-git-main-anishkganeshs-projects.vercel.app/login}
\end{center}

\end{document}