\documentclass[11pt]{article}
\usepackage[margin=0.9in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{pgfgantt}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tcolorbox}
\usepackage{fontawesome5}
\usepackage{tabularx}

% Define colors
\definecolor{lithosblue}{RGB}{59, 130, 246}
\definecolor{lithosdark}{RGB}{15, 23, 42}
\definecolor{lithoslight}{RGB}{248, 250, 252}
\definecolor{lithosgreen}{RGB}{34, 197, 94}
\definecolor{lithosorange}{RGB}{251, 146, 60}

% Custom environments
\newtcolorbox{highlight}{
    colback=lithoslight,
    colframe=lithosblue,
    boxrule=0pt,
    left=2mm,
    right=2mm,
    top=1mm,
    bottom=1mm,
    arc=2mm,
    fontupper=\small
}

\newtcolorbox{metricbox}[1][]{
    colback=white,
    colframe=lithosblue!30,
    boxrule=1pt,
    left=3mm,
    right=3mm,
    top=2mm,
    bottom=2mm,
    arc=3mm,
    title=#1,
    fonttitle=\bfseries\color{lithosdark}
}

% Remove default indentation
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.8em}

% Custom section formatting
\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\Large\bfseries\color{lithosdark}}
  {\thesection}{1em}{}[\color{lithosblue}\titlerule]
  
\titleformat{\subsection}
  {\normalfont\large\bfseries\color{lithosdark}}
  {\thesubsection}{1em}{}

\title{\vspace{-2cm}\textbf{\Huge Lithos AI}\\[0.5em]
\Large\color{lithosdark} Technical Architecture for VIP-X Accelerator\\[0.3em]
\normalsize\color{lithosdark} Mining Intelligence Platform}
\author{Anish Ganesh (SEAS '26) \& Kamal Kadiri (WG '26)}
\date{}

\begin{document}

\maketitle
\vspace{-1cm}

\begin{highlight}
\textbf{Executive Summary:} Lithos AI transforms mining documentation into actionable intelligence. Built in 7 days, processing 92\% accuracy, serving real-time insights to investment teams tracking 100+ mining assets globally.
\end{highlight}

%==============================================================================
\section{Product Architecture}
%==============================================================================

Our platform leverages modern web technologies to deliver institutional-grade mining intelligence. The architecture prioritizes real-time data processing, scalability, and user experience.

\begin{center}
\begin{tikzpicture}[
    node distance=1.5cm,
    box/.style={rectangle, draw=lithosblue, fill=white, text width=3cm, text centered, minimum height=1cm, rounded corners=2mm},
    databox/.style={rectangle, draw=lithosgreen, fill=lithosgreen!10, text width=2.5cm, text centered, minimum height=0.8cm, rounded corners=2mm},
    arrow/.style={->, >=stealth, thick, color=lithosblue!70}
]
    % User Layer
    \node[box] (ui) at (0,4) {\textbf{React UI}\\Next.js 15};
    \node[box] (screener) at (3.5,4) {\textbf{Screener}\\1000+ Projects};
    \node[box] (chat) at (7,4) {\textbf{AI Chat}\\GPT-4o-mini};
    
    % API Layer
    \node[box, text width=10cm] (api) at (3.5,2) {\textbf{API Routes \& Processing Pipeline}\\SSE Streaming • WebSocket • REST};
    
    % Data Layer
    \node[databox] (supabase) at (0,0) {\textbf{Supabase}\\PostgreSQL};
    \node[databox] (firecrawl) at (3.5,0) {\textbf{Firecrawl}\\Web Scraping};
    \node[databox] (openai) at (7,0) {\textbf{OpenAI}\\Extraction};
    
    % Connections
    \draw[arrow] (ui) -- (api);
    \draw[arrow] (screener) -- (api);
    \draw[arrow] (chat) -- (api);
    \draw[arrow] (api) -- (supabase);
    \draw[arrow] (api) -- (firecrawl);
    \draw[arrow] (api) -- (openai);
\end{tikzpicture}
\end{center}

The system processes mining documents through a sophisticated pipeline: web scraping via Firecrawl, AI extraction using GPT-4o-mini, and real-time delivery through Server-Sent Events. Our React frontend provides instant filtering across 20+ data dimensions while maintaining sub-200ms response times.

%==============================================================================
\section{Week 1 Sprint: Concept to Production}
%==============================================================================

\begin{center}
\begin{tikzpicture}[x=2cm, y=1.5cm]
    % Timeline base
    \draw[line width=2pt, color=lithosdark!30] (0,0) -- (7,0);
    
    % Day markers
    \foreach \x in {0,...,7} {
        \draw[line width=1.5pt, color=lithosdark] (\x,-0.15) -- (\x,0.15);
        \node[below, font=\footnotesize\bfseries] at (\x,-0.35) {Day \x};
    }
    
    % Development phases with bars
    % Day 0-1: Setup
    \fill[lithosblue!60, rounded corners=2pt] (0,0.2) rectangle (1.8,0.6);
    \node[above, font=\footnotesize\bfseries, color=lithosdark] at (0.9,0.6) {Setup Framework};
    
    % Day 2-3: Screener
    \fill[lithosgreen!60, rounded corners=2pt] (1.2,0.2) rectangle (3.2,0.6);
    \node[above, font=\footnotesize\bfseries, color=lithosdark] at (2.2,0.6) {Screener Table};
    
    % Day 3-4: Detail Panel  
    \fill[lithosorange!60, rounded corners=2pt] (2.8,0.2) rectangle (4.5,0.6);
    \node[above, font=\footnotesize\bfseries, color=lithosdark] at (3.65,0.6) {Detail Panel};
    
    % Day 4-5: Mining Agent
    \fill[lithosblue!60, rounded corners=2pt] (4,0.2) rectangle (5.8,0.6);
    \node[above, font=\footnotesize\bfseries, color=lithosdark] at (4.9,0.6) {Mining Agent};
    
    % Day 5-6: Chat Interface
    \fill[lithosgreen!60, rounded corners=2pt] (5.2,0.2) rectangle (6.8,0.6);
    \node[above, font=\footnotesize\bfseries, color=lithosdark] at (6,0.6) {Chat AI};
    
    % Day 6-7: Integration
    \fill[lithosdark!40, rounded corners=2pt] (6.2,0.2) rectangle (7,0.6);
    \node[above, font=\footnotesize\bfseries, color=lithosdark] at (6.6,0.6) {Integration};
    
    % Completion indicator
    \draw[line width=3pt, color=lithosgreen, ->] (0,-0.8) -- (7,-0.8) node[right, font=\small\bfseries] {100\% Complete};
\end{tikzpicture}
\end{center}

\subsection{Performance Metrics Achieved}

\begin{center}
\begin{tabularx}{\textwidth}{X X X X}
\toprule
\textbf{Metric} & \textbf{Target} & \textbf{Achieved} & \textbf{Status} \\
\midrule
Document Processing & <90s & 60s & \textcolor{lithosgreen}{\faCheckCircle} \\
Extraction Accuracy & >85\% & 92\% & \textcolor{lithosgreen}{\faCheckCircle} \\
UI Response Time & <300ms & 200ms & \textcolor{lithosgreen}{\faCheckCircle} \\
Projects per Run & 5-10 & 8 avg & \textcolor{lithosgreen}{\faCheckCircle} \\
\bottomrule
\end{tabularx}
\end{center}

%==============================================================================
\section{Technical Implementation}
%==============================================================================

\subsection{Core Innovation: Mining Agent Pipeline}

The Mining Agent represents our proprietary approach to automated intelligence gathering. It orchestrates multiple components in a synchronized pipeline that delivers real-time insights.

\begin{metricbox}[Mining Agent Architecture]
\textbf{Query Generation} $\rightarrow$ \textbf{Web Scraping} $\rightarrow$ \textbf{AI Extraction} $\rightarrow$ \textbf{Data Enrichment} $\rightarrow$ \textbf{Database Sync}

Each stage operates concurrently with retry logic, processing 5 documents in parallel while maintaining data consistency through PostgreSQL transactions.
\end{metricbox}

Our extraction algorithm leverages GPT-4o-mini with custom prompts optimized for mining terminology. The system identifies and extracts 30+ fields from technical reports including NPV, IRR, resource estimates, and production timelines with 92\% accuracy.

\subsection{Real-time Data Synchronization}

The platform maintains data freshness through three synchronized mechanisms:

\textbf{Supabase Realtime} provides WebSocket subscriptions for instant database updates. When new projects enter the system, connected clients receive updates within 500ms.

\textbf{Custom Event Broadcasting} enables cross-component communication through a lightweight event system. The mining agent dispatches progress events that update the UI without page refreshes.

\textbf{Server-Sent Events} stream extraction progress to users, providing detailed status updates including source identification, document processing, and project discovery notifications.

%==============================================================================
\section{In-House vs Outsourced Development Strategy}
%==============================================================================

\subsection{Why 100\% In-House Development}

Our technical team possesses the complete skill set required to build and scale Lithos without external development resources. This strategic decision accelerates development, reduces costs, and maintains intellectual property control.

\begin{metricbox}[Core Competencies Enabling In-House Development]
\textbf{Full-Stack Engineering:} Proficiency in React, Next.js, TypeScript, and Node.js eliminates need for frontend contractors\\[0.3em]
\textbf{AI/ML Expertise:} Direct experience with OpenAI APIs and prompt engineering removes requirement for ML consultants\\[0.3em]
\textbf{Data Engineering:} PostgreSQL, PostGIS, and real-time systems knowledge avoids database specialist costs\\[0.3em]
\textbf{Domain Knowledge:} Deep understanding of mining industry workflows prevents need for domain consultants
\end{metricbox}

\subsection{Development Timeline Comparison}

\begin{center}
\begin{tikzpicture}[x=0.8cm, y=0.6cm]
    % In-House Timeline
    \node[left, font=\bfseries] at (0,3) {In-House:};
    \draw[line width=2pt, color=lithosgreen!30] (0,3) -- (12,3);
    \fill[lithosgreen, rounded corners] (0,2.7) rectangle (1,3.3);
    \node[below, font=\tiny] at (0.5,2.6) {Week 1};
    \fill[lithosgreen, rounded corners] (1.2,2.7) rectangle (4,3.3);
    \node[below, font=\tiny] at (2.6,2.6) {Month 1};
    \fill[lithosgreen, rounded corners] (4.2,2.7) rectangle (12,3.3);
    \node[below, font=\tiny] at (8,2.6) {Months 2-6};
    \node[right, font=\small\bfseries, color=lithosgreen] at (12.2,3) {Production Ready};
    
    % Outsourced Timeline (hypothetical)
    \node[left, font=\bfseries] at (0,1) {Outsourced:};
    \draw[line width=2pt, color=lithosorange!30] (0,1) -- (16,1);
    \fill[gray, rounded corners] (0,0.7) rectangle (2,1.3);
    \node[below, font=\tiny] at (1,0.6) {Vendor Selection};
    \fill[gray, rounded corners] (2.2,0.7) rectangle (4,1.3);
    \node[below, font=\tiny] at (3,0.6) {Contracts};
    \fill[lithosorange, rounded corners] (4.2,0.7) rectangle (8,1.3);
    \node[below, font=\tiny] at (6,0.6) {Development};
    \fill[lithosorange, rounded corners] (8.2,0.7) rectangle (12,1.3);
    \node[below, font=\tiny] at (10,0.6) {Integration};
    \fill[gray, rounded corners] (12.2,0.7) rectangle (16,1.3);
    \node[below, font=\tiny] at (14,0.6) {Knowledge Transfer};
    \node[right, font=\small\bfseries, color=lithosorange] at (16.2,1) {8+ Months};
\end{tikzpicture}
\end{center}

\subsection{Cost Analysis: In-House Advantage}

\begin{center}
\begin{tabularx}{\textwidth}{X r r r}
\toprule
\textbf{Component} & \textbf{In-House Cost} & \textbf{Outsourced Cost} & \textbf{Savings} \\
\midrule
Frontend Development & \$0 (existing team) & \$30,000 & \$30,000 \\
Backend Architecture & \$0 (existing team) & \$40,000 & \$40,000 \\
AI Integration & \$0 (existing team) & \$25,000 & \$25,000 \\
Database Design & \$0 (existing team) & \$15,000 & \$15,000 \\
Project Management & \$0 (founders) & \$20,000 & \$20,000 \\
\midrule
\textbf{Total Development} & \textbf{\$0} & \textbf{\$130,000} & \textbf{\$130,000} \\
\bottomrule
\end{tabularx}
\end{center}

\subsection{Strategic Benefits of In-House Development}

\textbf{Velocity \& Iteration Speed}\\
Direct control over the codebase enables rapid iteration based on customer feedback. We deployed 15 updates in Week 1 alone—impossible with external vendors requiring change requests and approval cycles.

\textbf{IP Protection \& Competitive Moat}\\
Our proprietary mining agent algorithms and extraction logic remain confidential. No exposure to third-party developers who might replicate our approach for competitors.

\textbf{Quality \& Technical Debt}\\
Founders writing production code ensures architectural decisions align with long-term vision. No shortcuts or suboptimal patterns introduced by contractors optimizing for project completion rather than maintainability.

\textbf{Customer Responsiveness}\\
When a customer reports an issue or requests a feature, we can deploy fixes within hours. External development would require tickets, prioritization meetings, and multi-day turnaround times.

\subsection{Technical Stack Mastery}

Our team's existing proficiency eliminates the learning curve typically associated with new projects:

\begin{highlight}
\faCheckCircle \quad \textbf{Next.js 15:} 3+ years experience, deployed 10+ production applications\\
\faCheckCircle \quad \textbf{React/TypeScript:} 5+ years, including complex state management\\
\faCheckCircle \quad \textbf{PostgreSQL:} Advanced query optimization, PostGIS spatial queries\\
\faCheckCircle \quad \textbf{AI/ML:} Published research, production GPT implementations\\
\faCheckCircle \quad \textbf{Real-time Systems:} WebSocket, SSE, and streaming architectures
\end{highlight}

%==============================================================================
\section{Development Roadmap}
%==============================================================================

\begin{center}
\begin{tikzpicture}[scale=0.9]
    % Months timeline
    \draw[thick, ->, color=lithosdark] (0,0) -- (13,0) node[right] {Months};
    \foreach \x in {1,2,...,12} {
        \draw (\x,0.1) -- (\x,-0.1) node[below] {\x};
    }
    
    % Phase 1: Foundation
    \fill[lithosblue!30, rounded corners] (0.5,0.5) rectangle (2.5,1.5);
    \node[align=center] at (1.5,1) {\textbf{Phase 1}\\Foundation};
    
    % Phase 2: Enhancement
    \fill[lithosgreen!30, rounded corners] (3,0.5) rectangle (6,1.5);
    \node[align=center] at (4.5,1) {\textbf{Phase 2}\\Analytics};
    
    % Phase 3: Enterprise
    \fill[lithosorange!30, rounded corners] (6.5,0.5) rectangle (9.5,1.5);
    \node[align=center] at (8,1) {\textbf{Phase 3}\\Enterprise};
    
    % Phase 4: Scale
    \fill[lithosblue!30, rounded corners] (10,0.5) rectangle (12.5,1.5);
    \node[align=center] at (11.25,1) {\textbf{Phase 4}\\Scale};
\end{tikzpicture}
\end{center}

\textbf{Months 1-2: Enhanced Data Pipeline}\\
Implement advanced OCR for legacy documents, achieving 97\% accuracy on historical reports. Deploy multi-source validation across SEDAR+, SEC EDGAR, and ASX databases.

\textbf{Months 3-4: Predictive Analytics}\\
Launch ML models for project success scoring. Integrate commodity price feeds and develop portfolio optimization algorithms for investment teams.

\textbf{Months 5-6: Enterprise Integration}\\
Build Salesforce and HubSpot connectors. Implement team collaboration features including shared watchlists and annotation systems.

\textbf{Months 7-12: Market Expansion}\\
Scale to process 1M+ documents monthly. Launch white-label solutions for investment banks. Achieve SOC 2 compliance certification.

%==============================================================================
\section{Financial Projections}
%==============================================================================

\subsection{6-Month Operating Budget}

\begin{center}
\begin{tikzpicture}
    \pie[text=legend, radius=2, color={lithosblue!70, lithosgreen!70, lithosorange!70, lithosdark!30}]{
        30/Infrastructure \& APIs,
        35/Development Resources,
        20/Data Sources,
        15/Marketing \& Sales
    }
\end{tikzpicture}
\end{center}

\begin{metricbox}[Investment Allocation]
\begin{tabularx}{\textwidth}{X r}
\textbf{Infrastructure \& APIs} & \$18,000 \\
\quad Firecrawl, OpenAI, Supabase, Hosting & \\[0.3em]
\textbf{Development Resources} & \$21,000 \\
\quad Engineering, Design, QA Testing & \\[0.3em]
\textbf{Premium Data Sources} & \$12,000 \\
\quad SEDAR+, SEC EDGAR, Market Feeds & \\[0.3em]
\textbf{Go-to-Market} & \$9,000 \\
\quad Customer Acquisition, Conferences & \\[0.3em]
\midrule
\textbf{Total 6-Month Budget} & \textbf{\$60,000} \\
\end{tabularx}
\end{metricbox}

\subsection{Revenue Projections}

Based on our customer research with 23 investment professionals, we project conservative growth targeting mid-cap royalty and streaming firms managing \$150M-\$750M portfolios.

\begin{center}
\begin{tabularx}{\textwidth}{l X r r}
\toprule
\textbf{Quarter} & \textbf{Target Segment} & \textbf{Customers} & \textbf{MRR} \\
\midrule
Q1 2025 & Early Adopters & 5 & \$25,000 \\
Q2 2025 & Royalty \& Streaming & 15 & \$75,000 \\
Q3 2025 & Investment Banks & 30 & \$150,000 \\
Q4 2025 & Enterprise Expansion & 50+ & \$250,000 \\
\bottomrule
\end{tabularx}
\end{center}

%==============================================================================
\section{Technical Differentiators}
%==============================================================================

\begin{highlight}
Our platform uniquely combines real-time document processing, AI-powered extraction, and institutional-grade analytics in a single interface. While competitors focus on data aggregation, Lithos delivers actionable intelligence with source-level auditability.
\end{highlight}

\textbf{Speed Advantage}\\
Process technical reports in 60 seconds versus 4-6 hours manual review. Our parallel processing architecture handles multiple documents simultaneously while maintaining 92\% extraction accuracy.

\textbf{Intelligence Layer}\\
Beyond data extraction, we provide context through industry defaults, peer comparisons, and trend analysis. Each data point links to its source document, ensuring complete auditability for investment committees.

\textbf{User Experience}\\
Built by analysts for analysts. Every feature addresses specific workflow pain points identified through 23 customer interviews. The interface prioritizes information density while maintaining clarity.

%==============================================================================
\section{Team Execution Capability}
%==============================================================================

Our rapid development from concept to production in 7 days demonstrates exceptional execution velocity. The technical architecture supports immediate scaling without fundamental restructuring.

\begin{metricbox}[Week 1 Achievements]
\faCode \quad 15,000+ lines of production code\\
\faDatabase \quad 3 database migrations with PostGIS integration\\
\faRobot \quad 5 AI models integrated and optimized\\
\faUsers \quad 3 complete user interfaces deployed\\
\faServer \quad 10+ API endpoints with streaming support
\end{metricbox}

This development velocity, combined with deep domain expertise and direct customer feedback, positions Lithos to capture significant market share in the \$60B mining investment sector.

%==============================================================================
\section{Conclusion}
%==============================================================================

Lithos AI addresses a critical gap in mining intelligence infrastructure. Investment teams currently lose 6-17 weeks annually to manual data gathering. Our platform recovers this time while improving decision quality through comprehensive, real-time intelligence.

With VIP-X support, we will accelerate our roadmap, expand data coverage, and establish Lithos as the definitive intelligence platform for mining investment professionals. Our technical foundation, proven execution capability, and validated market demand create a compelling opportunity for transformative growth.

\vspace{1cm}
\begin{center}
\begin{tcolorbox}[colback=lithosblue!5, colframe=lithosblue, boxrule=2pt, arc=3mm, width=0.8\textwidth]
\centering
\textbf{\Large Ready to Transform Mining Intelligence}\\[0.5em]
\textcolor{lithosdark}{7 days from concept to production}\\
\textcolor{lithosdark}{92\% extraction accuracy}\\
\textcolor{lithosdark}{\$2M ARR projected Year 1}
\end{tcolorbox}
\end{center}

\end{document}